Resistive magneto-rotational instability in massive protoplanetary disks

### 2013-10-23 paper/setup.tex
minor paper update
minor tex update

\subsection{Resistivity profile}
Following \cite{fleming03}, we adopt the resistivity profile
\begin{align}
  \eta(z) =
  \sqrt{2}\eta_0\left[\exp{\left(-g_+\right)}+\exp{\left(-g_-\right)}\right]^{-1/2},  
\end{align}
where
\begin{align}
  &g_\pm(z) =  \frac{\Sigma_\pm(z)-\Sigma_0}{\Sigma_*}, \\
  &\Sigma_\pm(z) = \int_{\pm z}^\infty\rho(z^\prime)dz^\prime, \label{sigma_pm}
\end{align}
and $\Sigma_0\equiv\Sigma_{\pm}(0)$, so that $g_\pm(0)=0$ and $\eta_0 
= \eta(0)$. The constant $\Sigma_*$ is chosen such that 
\begin{align}
  \cosh{\left(\frac{\Sigma_0}{\Sigma_*}\right)} =
  \left[\frac{\eta_0}{\eta(\infty)}\right]^2,
\end{align}
and we define $\eta_0/\eta(\infty)\equiv A$ as the conductivity
boost factor from the midplane to the disk surface. We remark that
once the equilibrium $\rho$ and $d\rho/dz$ are obtained from
Eq. \ref{eqm_eqns1} --- \ref{eqm_eqns2}, the integration for
Eq. \ref{sigma_pm} can be done implicitly by using the Poisson
equation.

>>>>

\subsection{Resistivity profile}\label{resis_profile}
Following \cite{fleming03}, we adopt the resistivity profile
\begin{align}
  \eta(z) =
  \sqrt{2}\eta_0\left[\exp{\left(-g_+\right)}+\exp{\left(-g_-\right)}\right]^{-1/2},  
\end{align}
where
\begin{align}
  &g_\pm(z) =  \frac{\Sigma_\pm(z)-\Sigma_0}{\Sigma_*}, \\
  &\Sigma_\pm(z) = \int_{\pm z}^\infty\rho(z^\prime)dz^\prime, \label{sigma_pm}
\end{align}
and $\Sigma_0\equiv\Sigma_{\pm}(0)$, so that $g_\pm(0)=0$ and $\eta_0 
= \eta(0)$. The constant $\Sigma_*$ is chosen such that 
\begin{align}
  \cosh{\left(\frac{\Sigma_0}{\Sigma_*}\right)} =
  \left[\frac{\eta_0}{\eta(\infty)}\right]^2,
\end{align}
and we define $\eta_0/\eta(\infty)\equiv A$ as the conductivity
boost factor from the midplane to the disk surface. We remark that
once the equilibrium $\rho$ and $d\rho/dz$ are obtained from
Eq. \ref{eqm_eqns1} --- \ref{eqm_eqns2}, the integration for
Eq. \ref{sigma_pm} can be done implicitly by using the Poisson
equation.

Example resistivity profiles are shown in Fig. \ref{eqm_resis} for the isothermal disk. 
The midplane Elsasser number is $\Lambda(0)=0.1$ and the conductivity is boosted by a factor $A=10$ 
from the midplane to the upper disk boundary. The figure compares a strongly self-gravitating case
($Q=0.2$) and the non-self-gravitating limit ($Q=10$).

\begin{figure}
  \includegraphics[width=\linewidth]{figures/elsasser_iso}
  \caption{Elsasser number as prescribed in \S\ref{resis_profile} for
    isothermal disks with $Q=0.2$ (solid) 
    and $Q=10$ (dotted). The vertical line
    indicates $\Lambda=1$ in each case. \label{eqm_resis}}
\end{figure}
